Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-12-11 paper/main.tex
also plot morse potential and adjust figure caption

\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.3\textwidth]
        {docs/source/_static/mechanics.pdf}
        \node at (0, 1)[anchor=north west]{\textbf{A}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.3\textwidth]
        {docs/source/_static/interaction.pdf}
        \node at (0, 1)[anchor=north west]{\textbf{B}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.3\textwidth]
        {docs/source/_static/mie-potential-shapes.pdf}
        \node at (0, 1)[anchor=north west]{\textbf{C}};
    \end{tikzonimage}%
    \caption{
        (A) Example of an elonged bacterial rod represented by a collection of vertices which are
        connected by springs.
        The angles $\alpha_i$ will be used to model the rigidity of the rod.
        A bacterial agent which is not interacting with any external objects will tend to the
        equilibrium state of a straight rod with no curvature.
        (B) Potential curves of the Mie potential for various combinations of exponents $n,m$ with
        upper bound $\beta=2.5U_0$ and cutoff $\zeta=3(R_1+R_2)$.
    }
    \label{fig:model-bacterium}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.5\textwidth]
        {docs/source/_static/mechanics.pdf}
        \node at (0, 1)[anchor=north west]{\textbf{A}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.5\textwidth]
        {docs/source/_static/interaction.pdf}
        \node at (0, 1)[anchor=north west]{\textbf{B}};
    \end{tikzonimage}\\
    \begin{tikzonimage}[width=0.5\textwidth]
        {docs/source/_static/mie-potential-shapes.pdf}
        \node at (0, 1)[anchor=north west]{\textbf{C}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.5\textwidth]
        {docs/source/_static/morse-potential-shapes.pdf}
        \node at (0, 1)[anchor=north west]{\textbf{D}};
    \end{tikzonimage}%
    \caption{
        (A) Example of an elonged bacterial rod represented by a collection of vertices which are
        connected by springs.
        The angles $\alpha_i$ will be used to model the rigidity of the rod.
        A bacterial agent which is not interacting with any external objects will tend to the
        equilibrium state of a straight rod with no curvature.
        (B) Schematic of calculating the physical interaction between two bacteria.
        Vertices on the upper agent are interacting with nearest points on the polygon by the lower
        agent.
        (C) Potential curves of the Mie potential for various combinations of exponents $n,m$ with
        upper bound $\beta=2.5U_0$ and cutoff $\zeta=3.5(R_1+R_2)$.
        (D) Potential curves of the Morse potential with various stiffnesses $\omega$ and cutoff
        $\zeta=3.5(R_1+R_2)$.
    }
    \label{fig:model-bacterium}
\end{figure}
